\section{Model Evaluation and Further Discussion}
\subsection{Model Evaluation}

%6-1-1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Advantages}

\begin{itemize}[label=\Large\ding{117},leftmargin=*,itemsep=0.6ex,topsep=0.5ex]
    \item 双变量分布刻画磨损形态并匹配参数差异。
    \item 采用粒子群等优化提升拟合效率与精度。
    \item 将人群流量抽象为流体并用数值方法求解。
    \item 引入脉冲函数模拟短时大量人流场景。
    \item 模型方法成熟、准确性较高、可复用性强。
\end{itemize}




%6-1-2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Limitations}

\begin{itemize}[label=\Large\ding{117},leftmargin=*,itemsep=0.6ex,topsep=0.5ex]
    \item 现场测量手段有限，数据精度受约束。
    \item 样本场景单一，外推到多类楼梯存在偏差。
\end{itemize}


%6-2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Future Work}

%6-2-1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Model extension}


%6-2-2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Model application}










\section{Conclusions}














\cite{Krawitz2025}


\newpage

\addcontentsline{toc}{section}{Reference}
\renewcommand{\refname}{Reference}  % 英文环境用\refname
\begin{thebibliography}{99}
	

	
	\bibitem{Bundela2024}
	Bundela B, Sharma S, Singh B R.
	A Review Article on Relation between Mathematical Modelling and Machine Learning[J].
	Journal of China University of Mining \& Technology, 2024, 29(2): 123–129.
	
	\bibitem{Krawitz2025}
	Krawitz J, Schukajlow S, Yang X, et al. 
	A Systematic Review of International Perspectives on Mathematical Modelling: Modelling Goals and Task Characteristics[J]. 
	ZDM – Mathematics Education, 2025, 57: 193–212.
	
	
	
	
	
	\bibitem{Lyon2020}
	Lyon J A, Magana A J.
	A Review of Mathematical Modeling in Engineering Education[J].
	International Journal of Engineering Education, 2020, 36(1A): 101–116.
	
	\bibitem{Huang2022}
	Huang S, Feng W, Tang C, et al.
	Partial Differential Equations Meet Deep Neural Networks: A Survey[EB/OL].
	arXiv:2211.05567, 2022.
	
	\bibitem{Zino2021}
	Zino L, Cao M.
	Analysis, Prediction, and Control of Epidemics: A Survey from Scalar to Dynamic Network Models[EB/OL].
	arXiv:2103.00181, 2021.
	
	\bibitem{Turkey2023}
	Author Unknown.
	Review of Mathematical Modeling Research: A Descriptive Content Analysis[J].
	Balıkesir NEF Journal, 2023.
	
	\bibitem{SoftRobotics2023}
	Author Unknown.
	Mathematical modelling, analysis and control in soft robotics: a survey[J].
	Journal of the Brazilian Society of Mechanical Sciences and Engineering, 2023.
	
	\bibitem{PDE2012}
	Author Unknown.
	Mathematical Modelling at a Glance: A Theoretical Study[J].
	Procedia - Social and Behavioral Sciences, 2012, 46: 3980–3984.
	
	\bibitem{Surrogate2024}
	Author Unknown.
	A Review of Recent Advances in Surrogate Models for Uncertainty Quantification[J].
	Computer Methods in Applied Mechanics and Engineering, 2024.
	
\end{thebibliography}

































































\newpage
\section*{Appendices}
\addcontentsline{toc}{section}{Appendices}
